---
title: "Untitled"
author: "Georges Colbert"
date: "3/17/2018"
output: html_document
---


```{r }
library(readxl)
library(ggplot2)
library(dplyr)




################ the is the data taken from CCU01B class

Summary.b <- read_excel("Desktop/Projects/RAYSE ACADEMY/Untitled Folder/CCU01B/Khan Academy Report -- 03-16-1970 to 03-31-2018.xlsx", sheet = 'Summary')
Mission.specific.b <- read_excel("Desktop/Projects/RAYSE ACADEMY/Untitled Folder/CCU01B/Khan Academy Report -- 03-16-1970 to 03-31-2018.xlsx", sheet = "Mission-specific")
Exercises.b <- read_excel("Desktop/Projects/RAYSE ACADEMY/Untitled Folder/CCU01B/Khan Academy Report -- 03-16-1970 to 03-31-2018.xlsx", sheet = "Exercises")
Videos.b <- read_excel("Desktop/Projects/RAYSE ACADEMY/Untitled Folder/CCU01B/Khan Academy Report -- 03-16-1970 to 03-31-2018.xlsx", sheet = "Videos")
Points.b <- read_excel("Desktop/Projects/RAYSE ACADEMY/Untitled Folder/CCU01B/Khan Academy Report -- 03-16-1970 to 03-31-2018.xlsx", sheet = "Points")
Badges.b <- read_excel("Desktop/Projects/RAYSE ACADEMY/Untitled Folder/CCU01B/Khan Academy Report -- 03-16-1970 to 03-31-2018.xlsx", sheet = "Badges")
Skills.b <- read_excel("Desktop/Projects/RAYSE ACADEMY/Untitled Folder/CCU01B/Khan Academy Report Skill Progress.xlsx")


####Filter for  only the exercises that are part of the 3rd grade mission 

grade3.ex <- Exercises[Exercises$Exercise %in% Skills$Exercise,]





```


```{r }
#what is the one exercise in the 3rd grade mission that no student has yet attempted?

nrow(Skills.b)

length(unique(grade3b.ex$Exercise))

n <-   unique(grade3b.ex$Exercise)  
p <- Skills.b$Exercise


setdiff(p,n)




```


```{r}

######## Create a total minutes spent on Mission Collumn

ccu01b <- Mission.specific.b

m <- grade3b.ex %>% select(Student,`Time Spent (min)`) %>% group_by(Student) %>% summarise(total.minutes = sum(`Time Spent (min)`))

m <- as.data.frame(m)

ccu01b <- full_join(ccu01b,m, by="Student")

 
#####Creating a totalHours Collumn


myHours <- function (x) {
  return (x/60)
}

totalHours <- lapply(ccu01b$total.minutes, myHours)
totalHours <- unlist(totalHours)
ccu01b <- cbind(ccu01b,totalHours)



#### Summary of totalHours

summarise(ccu01b, maxHours=max(ccu01b$totalHours,na.rm=TRUE), medianhours=median(ccu01b$totalHours,na.rm=TRUE), meanHours=mean(ccu01b$totalHours,na.rm=TRUE))





```


Summary of hours spent by students on the Third grade mission

Maximum hours a student has spent on the platform is 47.8, the average hours students have spent is 1.51, the median is 14.85 the minimum is 0.


```{r }
###### Creating a Weeks Performing Collumn

myWeeks <- function (x) {
  return (x/3)
}

totalWeeks <- lapply(ccu01c$totalHours, myWeeks)
totalWeeks <- unlist(totalWeeks)
ccu01c<- cbind(ccu01c,totalWeeks)



summarise(ccu01c, max=max(ccu01c$totalWeeks,na.rm=TRUE), median=median(ccu01c$totalWeeks,na.rm=TRUE), mean=mean(ccu01c$totalWeeks,na.rm=TRUE))




```


summary of weeks spent by students on the third grade mission


Maximum amount of weeks, as defined by 3 hours per week, is 15.93 weeks on the 3rd grade mission. the median amount of weeks spent by students is 3.836, the average is 4.95. the minimum is 0.


```{r }
###### Creating a Weeks Performing Collumn

myWeeks <- function (x) {
  return (x/3)
}

totalWeeks <- lapply(ccu01b$totalHours, myWeeks)
totalWeeks <- unlist(totalWeeks)
ccu01b<- cbind(ccu01b,totalWeeks)



summarise(ccu01b, max=max(ccu01b$totalWeeks,na.rm=TRUE), median=median(ccu01b$totalWeeks,na.rm=TRUE), mean=mean(ccu01b$totalWeeks,na.rm=TRUE))





```




```{r }

########### Time Spent on Exercises

##### Overall Numbers for Time Spent on mission exercises

summarise(grade3b.ex, max = max(`Time Spent (min)`),
          min = min(`Time Spent (min)`),
          avg = mean(`Time Spent (min)`),)

### Time spent by
i <- grade3b.ex %>% select(Student,`Time Spent (min)` ) %>% group_by(Student) %>% summarise(Ex.time.max = max(`Time Spent (min)`),
                                                                                           Ex.time.min = min(`Time Spent (min)`),
                                                                                           ex.time.avg = mean(`Time Spent (min)`),
                                                                                           ex.time.median = median(`Time Spent (min)`))                                                                                   
                                                                                  

i <- as.data.frame(i)

ccu01b <- full_join(ccu01b,i, by="Student")


##### Summarize time spent per  Excercise

d <- grade3b.ex %>% select(Exercise,`Time Spent (min)` ) %>% group_by(Exercise) %>% summarise(Ex.time.max = max(`Time Spent (min)`),
                                                                                             Ex.time.min = min(`Time Spent (min)`),
                                                                                             ex.time.avg = mean(`Time Spent (min)`),
                                                                                             ex.time.median = median(`Time Spent (min)`)) 

head(d)





##### Create a progress collumn

nSkills <- nrow(Skills.b)

prog <- function (a,b,c,d,e) {
  mastered <- a *4
  level2 <- b *3
  level1 <- c * 1
  practiced <- d*1
  per <- (mastered+level2+level1+practiced)/(4*e)
  return(per)
  
}


Prog.b <- mapply(prog, Mission.specific.b$Mastered,
                   Mission.specific.b$`Level 2`, Mission.specific.b$`Level 1`, Mission.specific.b$Practiced, nSkills)

ccu01b <- cbind(ccu01b,Prog.b)

ccu01b <- ccu01b[order(ccu01b$Prog.b, decreasing = TRUE),]

head(ccu01b)









```

The following table is the top 5 exercises that have the most student with a struggling status.

```{r }

z <- filter(grade3b.ex, `Current Status`=='Struggling')

z <- table(z$Exercise)

z<- as.data.frame(z)

x <- filter(z, Freq>5)

x



```




```{r }


######################################################  Graphs  ###################################################### 

hist(ccu01b$Prog.b, main= "Distribution of Progress on 3rd grade mission #CCU01B")



plot(ccu01b$ex.time.avg,ccu01b$Prog.b, main= "Does  avg. time per Exercise on Mission. affect Progress #CCU01B", xlab="Ex. Time avg", ylab= " Progress" )

plot(ccu01b$ex.time.median,ccu01b$Prog.b, main= "Does median time per Ex. affect Progress #CCU01B", xlab="Ex. Time median", ylab= " Progress" )


hist(ccu01b$Prog.b, main= " Distribution of Progress #CCU01B")





```








