---
title: "Untitled"
author: "Georges Colbert"
date: "2/23/2018"
output:
  word_document: default
  pdf_document: default
---

```{r }
library(readxl)
library(ggplot2)
library(dplyr)
```


```{r }
library(readxl)
library(ggplot2)
library(dplyr)


################################ CCU01C MISSION: Third Grade


################  this is the data taken from CCU01C class

Summary <- read_excel("Khan Academy Report -- 02-17-1970 to 02-28-2018.xlsx", sheet = 'Summary')
Mission.specific <- read_excel("Khan Academy Report -- 02-17-1970 to 02-28-2018.xlsx", sheet = "Mission-specific")
Exercises <- read_excel("Khan Academy Report -- 02-17-1970 to 02-28-2018.xlsx", sheet = "Exercises")
Videos <- read_excel("Khan Academy Report -- 02-17-1970 to 02-28-2018.xlsx", sheet = "Videos")
Points <- read_excel("Khan Academy Report -- 02-17-1970 to 02-28-2018.xlsx", sheet = "Points")
Badges <- read_excel("Khan Academy Report -- 02-17-1970 to 02-28-2018.xlsx", sheet = "Badges")
Skills <- read_excel("Khan Academy Report Skill Progress.xlsx")



####Filter for  only the exercises that are part of the 3rd grade mission 

grade3.ex <- Exercises[Exercises$Exercise %in% Skills$Exercise,]




```



What is the one exercise in the 3rd grade mission that no student has yet attempted?

The number of exercises the students attempted is 114,but the total Skills in the Third Grade missions is 115.

"Telling time on the number line" is the one skill no student has yet attempted.


```{r }
#what is the one exercise in the 3rd grade mission that no student has yet attempted?

nrow(Skills)

length(unique(grade3.ex$Exercise))

n <-   unique(grade3.ex$Exercise)  
p <- Skills$Exercise


setdiff(p,n)





```


```{r }
######## Create a total minutes spent on Mission Collumn

ccu01c <- Mission.specific

m <- grade3.ex %>% select(Student,`Time Spent (min)`) %>% group_by(Student) %>% summarise(total.minutes = sum(`Time Spent (min)`))

m <- as.data.frame(m)

ccu01c <- full_join(ccu01c,m, by="Student")

#####Creating a totalHours Collumn


myHours <- function (x) {
  return (x/60)
}



totalHours <- lapply(ccu01c$total.minutes, myHours)
totalHours <- unlist(totalHours)
ccu01c <- cbind(ccu01c,totalHours)




```


Summary of hours spent by students on the Third grade mission

Maximum hours a student has spent on the platform is 39.5, the average hours students have spent is 15, the median is 11. the minimum is 0.


```{r }

#### Summarize of totalHours

summarise(ccu01c, maxHours=max(ccu01c$totalHours,na.rm=TRUE), medianhours=median(ccu01c$totalHours,na.rm=TRUE), meanHours=mean(ccu01c$totalHours,na.rm=TRUE))




```

summary of weeks spent by students on the third grade mission


Maximum amount of weeks, as defined by 3 hours per week, is 13 weeks on the 3rd grade mission. the median amount of weeks spent by students is 4, the average is 5. the minimum is 0.


```{r }
###### Creating a Weeks Performing Collumn

myWeeks <- function (x) {
  return (x/3)
}

totalWeeks <- lapply(ccu01c$totalHours, myWeeks)
totalWeeks <- unlist(totalWeeks)
ccu01c<- cbind(ccu01c,totalWeeks)



summarise(ccu01c, max=max(ccu01c$totalWeeks,na.rm=TRUE), median=median(ccu01c$totalWeeks,na.rm=TRUE), mean=mean(ccu01c$totalWeeks,na.rm=TRUE))




```

Time spent per exercise

the Maximum amount of time a student has spent on a exercise was 368.2, and the exercise was "Read bar graphs and solve 1-step problems". 

the average amount of time students have spent on a exercise is 12.27.




```{r }

########### Time Spent on Exercises

##### Overall Numbers for Time Spent on mission exercises

summarise(grade3.ex, max = max(`Time Spent (min)`),
          min = min(`Time Spent (min)`),
          avg = mean(`Time Spent (min)`),)



```



```{r }

### Time spent by
i <- grade3.ex %>% select(Student,`Time Spent (min)` ) %>% group_by(Student) %>% summarise(Ex.time.max = max(`Time Spent (min)`),
                                                                                      Ex.time.min = min(`Time Spent (min)`),
                                                                                      ex.time.avg = mean(`Time Spent (min)`),
                                                                                      ex.time.median = median(`Time Spent (min)`))                                                                                   



##### Summarize time spent per  Excercise

 d <- grade3.ex %>% select(Exercise,`Time Spent (min)` ) %>% group_by(Exercise) %>% summarise(Ex.time.max = max(`Time Spent (min)`),
                                                                                      Ex.time.min = min(`Time Spent (min)`),
                                                                                      ex.time.avg = mean(`Time Spent (min)`),
                                                                                      ex.time.median = median(`Time Spent (min)`)) 
i <- as.data.frame(i)

ccu01c <- full_join(ccu01c,i, by="Student")


##### Create a progress collumn

nSkills <- nrow(Skills)

prog <- function (a,b,c,d,e) {
  mastered <- a *4
  level2 <- b *3
  level1 <- c * 1
  practiced <- d*1
  per <- (mastered+level2+level1+practiced)/(4*e)
  return(per)
  
}


Progress <- mapply(prog, Mission.specific$Mastered,
                   Mission.specific$`Level 2`, Mission.specific$`Level 1`, Mission.specific$Practiced, nSkills)

ccu01c <- cbind(ccu01c,Progress)




ccu01c <- ccu01c[order(ccu01c$Progress, decreasing = TRUE),]


head(ccu01c)

```


The following table is the top 5 exercises that have the most student with a struggling status.

```{r }


###################### Find the exercise students struggle with the most

z <- filter(grade3.ex, `Current Status`=='Struggling')

z <- table(z$Exercise)

z<- as.data.frame(z)

x <- filter(z, Freq>5)

x

```




```{r }


######################################################  Graphs  ###################################################### 

######### breakdown of  current status
(bean <- table(grade3.ex$`Current Status`))


ggplot(grade3.ex,aes(grade3.ex$`Current Status`))+geom_bar()





hist(ccu01c$Progress, main= " Distribution of Progress on 3rd grade mission #CCU01C")



plot(ccu01c$ex.time.avg,ccu01c$Progress, main= "Does  avg. time per Ex. affect Progress #CCU01C", xlab="Ex. Time avg", ylab= " Progress" )

plot(ccu01c$ex.time.median,ccu01c$Progress, main= "Does median time per Ex. affect Progress #CCU01C", xlab="Ex. Time median", ylab= " Progress" )


########################  Time Series 


##### Time series of Student participation per day

grade3.ex$`Last Done` <- as.Date(grade3.ex$`Last Done`) 


d <- grade3.ex %>% select(`Last Done`,Student ) %>% group_by(`Last Done`) %>% summarise(nstudents= n_distinct(Student))


ggplot(d, aes(`Last Done`, nstudents)) + geom_line() +
  scale_x_date() + xlab("  ") + ylab(" # Students on KA ") + coord_cartesian(ylim = c(0, 11)) 



###### Time series of median time spent on KA per day


c <- grade3.ex %>% select(`Last Done`,`Time Spent (min)` ) %>% group_by(`Last Done`) %>% summarise(avg.time= median(`Time Spent (min)`))                                                                          




ggplot(c, aes(`Last Done`, avg.time)) + geom_line() +
  scale_x_date() + xlab("  ") + ylab(" Median Time Spent ") 



```





```{r }





```



```{r }





```



```{r }





```




```{r }





```








